### 2012-02-12 exam3/1.tex
Small fixes.

\item Some basic test taking advice: Before you start answering
any problems, read \emph{every} problem, so your brain can  think
about the harder problems in background while you knock off the easy ones.
\end{itemize}

@@

\item \verb|replace-gaga| - produces a \verb|P| with the \verb|gaga|
  field of any \verb|B| within this \verb|P| with a given string.

@@

Be sure to define any interfaces you need so that your program and say
which classes implement which interfaces so that your program treats
all values according to their interface.

>>>>

\item Some basic test taking advice: Before you start answering
any problems, read \emph{every} problem, so your brain can  think
about the harder problems in the background while you knock off the easy ones.
\end{itemize}

@@

\item \verb|replace-gaga| - produces a \verb|P| like this one, but
  with any \verb|gaga| field replaced by the given string.

@@

Be sure to define any interfaces you need and say which classes
implement which interfaces so that your program treats all values
according to their interface.
